When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed tense

Consequently, we had to adapt the MLM to incorporate this non-linear trend.
To apply the contrast to the $n$-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
$$
SV \sim level\ + d' + median RT + (1|subject)
$$
This means that the intercept still varies between subjects, but there are no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per $n$-back level per subject, rather than $n$-back levels per subject.
The ICC of the null model indicated that there is a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.2f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e. that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
We did not exclude any data points.
The results of the final model are displayed in Table\ \@ref(tab:H2b-results).

>>>>

Consequently, we had to adapt the MLM to incorporate this non-linear trend.
To apply the contrast to the $n$-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
$$
SV \sim level\ + d' + median RT + (1|subject)
$$
This means that the intercept still varied between subjects, but there were no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per $n$-back level per subject, rather than $n$-back levels per subject.
The ICC of the null model indicated that there was a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.2f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e. that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs could be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
We did not exclude any data points.
The results of the final model are displayed in Table\ \@ref(tab:H2b-results).
